---
title: "Inference - Comparisons"
author: "Mr. Adams"
date: "2/27/2019"
output: html_document
---

##install library 
```{r install libraries}

library(tidyverse)
library(skimr)
```

##Load your data

#Before going on, ensure that you have downloaded your data from Google clasroom and imported it into RStudio. 


##For this activity, we will be looking at data from a study that tested the effectiveness of nicotine lozenges (Siffman et al., 2002).

#What is the explanatory variable?

#What is the response variable?


##Create a 100% stacked graph to show the comparision between the proportions of people who abstained from smoking after taking a nicotine lozenge and taking a placebo lozenge.
```{r stacked graph}
result_ordered <- c("resumed", "abstained")
treatment_result <-  lozenge %>%
                    mutate(result = ordered(result, levels = result_ordered)) %>% 
                    arrange(result) %>%
                    ggplot(aes(x = treatment, fill = result)) +
                    geom_bar(position = "fill") +
                    labs(x = "Type of Lozenge")
treatment_result
```
## Create a two-way table 

```{r Create a two-way table}
treatment_totals <- lozenge %>%
            group_by(treatment, result) %>%
            summarize(num = n()) %>%
            spread(treatment, num)
treatment_totals
```

##In the space below cacluate the following:

#proportion of nicotine lozenge users who abstained from smoking
#proportion of placebo lozenge users who abstained from smoking
#combined proportion 
```{r calculating proportions}
prop_n_a <- 
prop_p_a <- 
prop_c <- 
  
props <- data.frame(prop_n_a,prop_p_a, prop_c)
props
```

##Check the technical conditions

```{r}

```

##Determine and interpret a 95% confidence interval for estimating the difference in population proptions showing successful abstinence between the two treatment groups. 

```{r}
two_prop_z <- prop.test(x = c(82, 44), n = c(459, 458), correct = FALSE, conf.level = 0.95)
two_prop_z
```

##Test of Significance 
#Write your null hypothesis

#Write your alternative hypothesis

#Using the output from the code above, write your test decision. 

# Write a sentence or two describing whether or not the difference in proportions is statistically significant. 



